Causal Bandits: Learning Good Interventions via Causal Inference

### 2016-02-05 causal-bandit/icml-2015/experiments.tex
updates

\begin{figure}[h]
\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=300$ and number of variables $N = 50$}
\label{fig:simple_vs_m}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_m_N50_T400_s100_20160205_1637.pdf}
\end{figure}

If figures \ref{fig:simple_vs_T_vary_epsilon} and \ref{fig:simple_vs_T} we compare the performance as a function of $T$. \todof{finish this}

>>>>

\begin{figure}[h]
\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$}
\label{fig:simple_vs_m}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_m_N50_T400_s100_20160205_1637.pdf}
\end{figure}

\begin{figure}[h]
\caption{Simple regret vs $m(\boldsymbol{q})$ for fixed horizon $T=400$ and number of variables $N = 50$, without truncation}
\label{fig:simple_vs_m2}
\centering
\includegraphics[width=.5\textwidth]{exp_regret_vs_m_N50_T400_s100_20160205_1701.pdf}
\end{figure}

If figures \ref{fig:simple_vs_T_vary_epsilon} and \ref{fig:simple_vs_T} we compare the performance as a function of $T$.
